\bf Visual Inference for Significance and Goodness-of-Fit Testing for a Social Network Model

### 2017-10-27 ASApaper/paper-child.Rnw
move content from experiment protocol section & delete that section

To construct a lineup, we simulate five networks from the null model and one network from the alternative model. We chose to expose our participants to only six plots at a time in order to show the node-link diagrams in more detail and to lower their cognitive load. Typically, lineup experiments are done with sets of 20 plots at a time c.f.~\citet{loy:2015, vanderplas:2016}, but we determined that not enough structure could be shown in each plot for 20 node-link diagrams. An example of a lineup like those shown to our participants is shown on the right side of the image  in Figure~\ref{fig:shiny}.  \footnote{If you would like to explore the lineups we use in further detail, please visit \url{https://sctyner.shinyapps.io/saom_lineup_creation/}}.

\begin{figure}
\includegraphics[width=.9\textwidth]{img/shinyappscreen.png}
\caption{\label{fig:shiny} A screen grab of the web application we created to design our lineup experiment. In this view, model M4 is selected and one estimate from model M4 with $\beta_5$ set to twice its estimated value given in Table~\ref{tab:effects} is placed at random among five observations simulated from model M1. The other two tabs in the right side of the screen tell you which plot comes from the alternative model, and allow you to view and download the data that is plotted in the lineup.}
\end{figure}

In model M1, with only two parameters in the objective function, we varied both the density and reciprocity parameteter values one at a time. In models M2 through M5, we vary the additional parameter, $\beta_3$ through $\beta_6$. Thus, we have six different parameters of interest to us: $\beta_1, \dots, \beta_6$. We want to determine how the size of these parameters affects the overall structure of the network data simulated from the models M1 through M5, so we also vary the value of the parameters in two directions: positive and negative.

@@

\subsection{Goodness-of-Fit}
\subsection{Visual Detection}

Through visual inference, we want to determine at which point an effect becomes noticeable in a SAOM. By \textit{noticeable}, we mean that the inclusion of the effect alters the appearance of networks simulated from a model. An effect becomes noticeable when a simulation from a model with a noticeable effect appears different from simulations from a model where the same affect is absent. %Because the traditional way to visualize a network is a node-link diagram, we will examine the effect of different parameter values using node-link visualizations.

@@

We showed participants from Amazon Mechanical Turk a series of lineups containing data simulated from M1 through M5.

@@

\section{Experiment Protocol}

>>>>

To construct a lineup, we simulate five networks from the null model and one network from the alternative model. We chose to expose our participants to only six plots at a time in order to show the node-link diagrams in more detail and to lower their cognitive load. Typically, lineup experiments are done with sets of 20 plots at a time c.f.~\citet{loy:2015, vanderplas:2016}, but we determined that not enough structure could be shown in each plot for 20 node-link diagrams. An example of a lineup like those shown to our participants is shown on the right side of the image  in Figure~\ref{fig:shiny}.  In this lineup, model M4 is the alternative model, and model M1 is the null model. To simulate lineups from the models, we set the parameters to the values given in Table~\ref{tab:fitted values} for all parameters within the respective models, with the exception of $\beta_5$. For $\beta_5$, twice the estimated value was used. More detail on why we use twice the fitted value is provided in Section~\ref{sec:setupvd}.\footnote{If you would like to explore the kinds of lineups we use in further detail, please visit \url{https://sctyner.shinyapps.io/saom_lineup_creation/}}. To get the simulations, we used the \tettt{siena07} function in \texttt{RSiena} \citep{RSiena}.

\begin{figure}
\includegraphics[width=.9\textwidth]{img/shinyappscreen.png}
\caption{\label{fig:shiny} A screen grab of the web application we created to design our lineup experiment. More details about this application are given in Section~\ref{sec:setupvd}. In the lineup, M4 is the alternative model and one estimate from model M4 with $\beta_5$ set to twice its estimated value given in Table~\ref{tab:fittedvalues} is placed at random among five observations simulated from the null model, M1. Which plot comes from model M4?  %The other two tabs in the right side of the screen tell you which plot comes from the alternative model, and allow you to view and download the data that is plotted in the lineup.
}
\end{figure}

We want to explore the role of each of these parameters in the objective functions for each model.

@@

\subsection{Goodness-of-Fit}
\subsection{Visual Detection}\label{sec:setupvd}

Through visual inference, we want to determine at which point an effect becomes noticeable in a SAOM. By \textit{noticeable}, we mean that the inclusion of the effect alters the appearance of networks simulated from a model. An effect becomes noticeable when a simulation from a model with a noticeable effect appears different from simulations from a model where the same affect is absent.
In model M1, with only two parameters in the objective function, we varied both the density and reciprocity parameteter values one at a time. In models M2 through M5, we vary the additional parameter, $\beta_3$ through $\beta_6$. Thus, we have six different parameters of interest to us: $\beta_1, \dots, \beta_6$. We want to determine how the size of these parameters affects the overall structure of the network data simulated from the models M1 through M5, so we also vary the value of the parameters in two directions: positive and negative.

%Because the traditional way to visualize a network is a node-link diagram, we will examine the effect of different parameter values using node-link visualizations.

@@

@@
